Response to reviewers

### 2022-02-08 response/response1.Rmd
minor changes to response letter

* We have corrected all minor grammatical errors pointed out by the reviewers.  
* We have made the descriptions of the steps more explicit.

@@

* We have made it explicit.

@@

\begin{description}
\item[Reviewer 2:]\textcolor{violet}{Before the data cleaning section I would love a glimpse into the future to see what the target dataset would look like. What are the observations? What are the variables? This would allow me to follow the narrative of data wrangling more easily. Perhaps this could be put into section 2.2, which is titled Target data. Then, when starting to describe the raw data in 3.1, explain the same pieces and explicitly explain why the raw data it is not tidy to begin with.}
\end{description}

@@

@@

* They are two different variables. We have separated it in the revised version.

>>>>

* We have corrected all minor grammatical errors pointed out by the reviewers as outlined below. [ADD the changes]  
* We have made the descriptions of the steps more explicit as follows [LIST OF THE CHANGES]

@@

* We have made the file format more explicit.

@@

@@

We agree that this level of precision was not necessary. We have modified Table 2 in line with this.

@@

* These are two different variables. We have made this easier to follow in the manuscript as: [FILL]
